---
title: "ISOM"
author: "pm"
date: '`r Sys.time()`'
output:
  pdf_document:
  keep_tex: yes
  number_sections: yes
html_document:
  highlight: espresso
  keep_md: yes
  number_sections: yes
  self_contained: no
  toc: yes
---
  
```{r, include=FALSE}
library(dplyr)
library(stringr)
library(magrittr)
load("Z:/Gesch\xe4ftsordnungen/database/aggregats/isord.Rdata")
```

```{r include=FALSE}
# version check 
data_path  <- "z:/gesch\u00e4ftsordnungen/database/extracts/"
db_on_disk_version <- 
  str_extract(list.files(data_path), "\\d+\\.\\d+") %>% 
  as.numeric()  %>% 
  max(na.rm=T)
db_on_disk_version
set.seed(7787)
options("width"=100)
```


# IDEP Standing Orders Minority-Majority-Change Dataset

The dataset is a compilation of data based on several data-sets: ERD [European Represantatives Dataset, Release 3, February 2014](http://www.erdda.se/index.php/projects/erd/data-archive), ISORD [IDEP Standing Orders Reform Dataset, version `r db_on_disk_version`](http://www.polver.uni-konstanz.de/sieberer/forschung/), ParlGov [Parliaments and governments database, 2012 release](http://www.parlgov.org/)



The data set incorporates aggregated data for 
`r dim(isord)[1] - length(unique(isord$country))` cabinets in
`r length(unique(substring(isord$country,1,3)))` countries and consists of 
`r dim(isord)[2]` variables. 

**Example:**
  
```{r, width=100}
isom  %>% 
  select(ctr, cab_pm, cab_in, wds_chg, pro_minmaj_qual, idl_pnt_all, volatility) %>% 
  mutate(
    idl_pnt_all = round(idl_pnt_all, 1), 
    volatility  = round(volatility, 1)
  )
```


# Variable Descriptions


## ERD variables




## ISORD variables

The variables of the ISORD dataset are extensively described in a seperate codebook. 


## ParlGov variables




## CMP variables 




















