---
title: "ISOM"
author: "pm"
date: '`r Sys.time()`'
output:
  pdf_document: null
  keep_tex: yes
  number_sections: yes
  html_document: default
html_document:
  highlight: espresso
  keep_md: yes
  number_sections: yes
  self_contained: no
  toc: yes
---
  
```{r, include=FALSE}
library(idep)
library(dplyr)
library(stringr)
library(magrittr)
load("Z:/Gesch\xe4ftsordnungen/database/aggregats/isom.Rdata")
```

```{r include=FALSE}
# version check 
data_path  <- "z:/gesch\u00e4ftsordnungen/database/extracts/"
db_on_disk_version <- 
  str_extract(list.files(data_path), "\\d+\\.\\d+") %>% 
  as.numeric()  %>% 
  max(na.rm=T)
db_on_disk_version
set.seed(7787)
options("width"=100)
Sys.setlocale("LC_TIME", "English")
```


# IDEP Standing Orders Minority-Majority-Change Dataset

The dataset is a compilation of data based on several data-sets: ERD [European Represantatives Dataset, Release 3, February 2014](http://www.erdda.se/index.php/projects/erd/data-archive), ISORD [IDEP Standing Orders Reform Dataset, version `r db_on_disk_version`](http://www.polver.uni-konstanz.de/sieberer/forschung/), ParlGov [Parliaments and governments database, 2012 release](http://www.parlgov.org/)

Its structure has several levels/layers -- time episodes for cabinets in different countries starting as early as `r format(min(isom$cab_in), "%B %Y")` up `r format(max(isom$cab_in), "%B %Y")`.

The basic structure of cabinet time episodes stems from ERD. Information on standing orders reforms was merged/joined from ISOR dataset by matching reform dates (date of acceptance of the reform or if not availible earliest date availible) into cabinet time spans (and countries). All measures of ideological positions, distances and polarization come from CMP which was merged/joined with ParlGov first (ParlGov includes the CMP party id variable). ParlGov in turn was used as source of volatility measures. Having merged/joined ParlGov and CMP this combined dataset was than joined with ERD by matching cabinet start dates (automatically and by hand due to occasional differing start days). 

The data set incorporates aggregated data for 
`r dim(isom)[1] - length(unique(isom$country))` cabinets in
`r length(unique(substring(isom$country,1,3)))` countries and consists of 
`r dim(isom)[2]` variables. 

**Example:**
  
```{r, width=100}
#### R-code: #### 

isom  %>% 
  select(ctr, cab_pm, cab_in, cab_out, wds_chg, pro_minmaj_qual, idl_pnt_all, volatility) %>% 
  mutate(
    idl_pnt_all = round(idl_pnt_all, 1), 
    volatility  = round(volatility, 1)
  )
```

# Citing the Data

Publications using this dataset should acknowledge in writing that the information comes from:

Andersson, Staffan; Bergman, Torbjörn; Ersson, Svante (2014). The European Representative Democracy Data Archive,
Release 3. Main sponsor: Riksbankens Jubileumsfond (In2007-0149:1-E). [www.erdda.se]

Döring, Holger; Manow, Philip (2015). Parliaments and governments database (ParlGov): Information on parties, elections and cabinets in modern democracies. Version: 2013.

Lehmann, Pola; Matthieß, Theres; Merz, Nicolas; Regel, Sven; Werner, Annika (2015): Manifesto Corpus. Version: 2013-b. Berlin: WZB Berlin Social Science Center.

Sieberer, Ulrich; Meißner, Peter; Keh, Julia; Müller, Wolfgang C. (2015): ISOR - IDEP Standing Orders Reforms Dateset. 

Sieberer, Ulrich; Meißner, Peter; Keh, Julia; Müller, Wolfgang C. (2015): ISOM - IDEP Standing Orders Minority-Majority Dateset. 

Tsebelis, George (2002): Veto Players. How Political Institutions Work. Princeton UP


# References used in the Codebook

**ERD:**

ERD (2014): European Representative Democracy (ERD) Release 3.0 February 12, 2014 Codebook for ERD - e. 


**CMP:**

CMP (2015): Manifesto Project Dataset Codebook. Website: https://manifesto-project.wzb.eu/ . Version: 2015a

**Volatility**

Pedersen, Mogens N. (1979): The Dynamics of European Party Systems: Changing Patterns of Electoral Volatility. European Journal of Political Research, 7/1, 1-26. http://janda.org/c24/Readings/Pedersen/Pedersen.htm


# Variable Descriptions

## Notes

The variables of the ISOR dataset are extensively described in a seperate codebook (`isor_codebook.pdf`) -- therefore only some of those variables are presented here. 

Since there might be more than one SO reform (ISOR) that took place during the course of a cabinet ISOR data had to be aggregated:

- all ISOR variables preserve their name 
- but if values had to be aggregated the variables names get an extra suffix:
    - **fst** for the value of the first reform of a cabinet time span
    - **lst** for the value of the last  reform of a cabinet time span
    - **mn**  for the mean value
    - **sum** for the sum of all values
- Furthermore, due to the aggregation of ISOR data an addtitional variable is provided: **n_reforms** captures the number of times SO were changed during the course of a cabinet. 
  
For a version of the very same data set prior to aggregation have a look at `isom_non_agg.Rdata` respectively `isom_non_agg.dta`. 

```{r Description Functions, include=FALSE}
sumdummy<-function(x){
  ifelse(
    class(x) == "character" | class(x) == "Date", 
    "-", 
    format(sum(x, na.rm=TRUE), scientific = F, big.mark = "\xA0") 
  )
}
sumvar <- function(x){
  cat("**`class    :`** `", 
      str_pad(class(x)               , 
              12, "left", "\u00A0") ,"`\\\n<br>")
  cat("**`unique   :`** `", 
      str_pad(length(unique(x))      , 
              12, "left", "\u00A0") ,"`\\\n<br>")
  cat("**`NAs      :`** `", 
      str_pad(sum(is.na(x))          , 
              12, "left", "\u00A0") ,"`\\\n<br>")
  cat("**`not-NA   :`** `", 
      str_pad(sum(!is.na(x))         , 
              12, "left", "\u00A0") ,"`\\\n<br>")
  cat("**`not-0-NA :`** `", 
      str_pad(sum(!is.na(x) & x!=0 ) , 
              12, "left", "\u00A0") ,"`\\\n<br>")
  cat("**`sum      :`** `", 
      str_pad(sumdummy(x)            , 
              12, "left", "\u00A0") ,"`\\\n<br>")
  cat(
      "**`range    :`** `[", 
    as.character(range(x, na.rm=T)[1]), 
    "] ... [",
    as.character(range(x, na.rm=T)[2]),
    "]",
    "`\\\n<br>"
  )
  cat(
      "**`examples :`** `", 
    paste0(substring(
      paste0("[",  paste(sample(x,10), collapse="], [", sep="") ,   "]"),
    0,80),""),
    "...",
    "`\\\n<br>"
  )
  
}
```



```{r Describing ERD, echo=FALSE, results='asis', warning=FALSE}
source("C:/Dropbox/RPackages/idep/inst/tasks/aggregate_data/variable_description_isom.r")
for( g in sort(unique(var_desc_erd$group)) ){
  gtitle <- str_replace(g, "^\\d* ", "")
  cat(paste0("\n## ", gtitle, "\n\n"))
  dat <- var_desc_erd  %>% filter(group==g)
  for( i in seq_len(dim(dat)[1]) ){
    cat(
      "\n\n**", dat$name[i], "** (", dat$from[i] ,")", "\n\n",
      dat$desc[i], "\n\n",
      sep=""
    )
    sumvar(as.data.frame(isom, stringsAsFactors=F)[ , dat$name[i] ])
    cat("\n\n<p>&nbsp;</p>")
  }
}
```
























